---
title: "Integration of the FIND graphic design in R Markdown reports"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(rmarkdown)
```

```{r development-1}
# Load already included functions
pkgload::load_all(export_all = FALSE)
```

# Create an HTML report

The `html_document_find()` function converts an .Rmd file to .html format. It admits `toc`, `toc_depth`, `toc_float` and `code_folding` arguments, similar to those of the `rmarkdown::html_document()` function, to control the appearance of the table of contents and code folding.

The `html_document_find()` function is called in the `output_format` argument of the `rmarkdown::render()` function.

```{r function-html_document_find}
#' Convert a .Rmd file into a .html file according to finddx design / template.
#'
#' @importFrom rmarkdown html_document
#'
#' @param toc Boolean. To include a table of contents in the output. Default is TRUE.
#' @param toc_depth Numeric. Depth of headers to include in table of contents. Default is 4.
#' @param toc_float Boolean. To float the table of contents to the left of the document. Default is TRUE.
#' @param code_folding Character. Enable document readers to toggle the display of R code chunks.
#' @param ... Additional arguments of \code{rmarkdown::\link{html_document}()}.
#' 
#' @return An R Markdown output format object
#' @export
html_document_find <- function(toc = TRUE, 
                               toc_depth = 4, 
                               toc_float = TRUE, 
                               code_folding = "show", 
                               ...) {

  css <- system.file("css", "main.css", package = "finddxtemplate")
  html_template <- system.file("html_template.html", package = "finddxtemplate")

  html_document(
    css = css,
    template = html_template,
    toc = toc,
    toc_depth = toc_depth,
    toc_float = toc_float,
    code_folding = code_folding,
    mathjax = NULL,
    ...
  )
}
```

```{r examples-html_document_find, eval=FALSE}
# Store in temp file for the example
rmddir <- tempfile(pattern = "rmd-")
dir.create(rmddir)

# Knit
rmarkdown::render(input = system.file("rmarkdown", "rmd_template.Rmd", package = "finddxtemplate"), 
                  output_format = html_document_find(),
                  output_dir = rmddir)

# Open the knitted example
browseURL(file.path(rmddir, "rmd_template.html"))
```

```{r tests-html_document_find}
expect_render <- function(template, FUN){

  render_dir <- tempfile()

  dir.create(render_dir)
  dir.create(file.path(render_dir, "www"))

  file.copy(
    system.file("rmarkdown", template, package = "finddxtemplate"),
    render_dir
  )

  file <- file.path(render_dir, template)

  expect_output(
    expect_message(
      rmarkdown::render(
        input = file,
        output_format = FUN,
        output_dir = render_dir),
      "Output created"
    ),
    "pandoc"
  )
}

test_that("html_document_find works", {
  expect_render(
    template = "rmd_template.Rmd", 
    FUN = html_document_find()
  )
})
```

Alternatively, you can change the `output` field in the YAML header of your .Rmd file:
```{r eval=FALSE}
---
title: "My report"
author: "Arthur Bréant"
date: "1/13/2022"
output: finddxtemplate::html_document_find
---
```

# Add a logo in the HTML report

You can add a logo with through the `logo` field in the yml header of your .Rmd file. It takes the path to the image file. Here, the logo is the one saved in the `{finddxtemplate}` package:

```{r eval=FALSE}
logo: "`r system.file('logo', 'logo.svg', package = 'finddxtemplate')`"
```

```{r eval=FALSE}
---
title: "My report"
author: "Arthur Bréant"
date: "1/13/2022"
logo: "`r system.file('logo', 'logo.svg', package = 'finddxtemplate')`"
output: finddxtemplate::html_document_find
---
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_html_document_find.Rmd",
  vignette_name = "b - create html documents",
  overwrite = "yes",
  check = FALSE
)
```
